Homework 1-- wilsonka
========================================================

1. Use the GEOmetabd package to find all HCV gene expression data using the Illumina platform submitted by an investigator at Yale. This should be done with a single query, showing the title, the GSE accession number, the GPL accession number and the manufacturer and the description of the platform used.

```{r message=FALSE}
library(GEOmetadb)
library(data.table)
```

```{r}
geo_con <- dbConnect(SQLite(),'GEOmetadb.sqlite')
```

```{r}
res <- dbGetQuery(geo_con, "SELECT DISTINCT gse.gse, gse.title, gpl.gpl, gpl.manufacturer, gpl.description FROM gse JOIN gse_gpl ON gse.gse=gse_gpl.gse JOIN gpl ON gse_gpl.gpl=gpl.gpl WHERE gse.pubmed_id='23067362'AND gpl.manufacturer like '%Illumina%';")
res
```


2. Reproduce your above query using the data.table package. Again, try to use a single line of code. [Hint: You first need to convert all db tables to data.table tables].

This sets-up the data tables used for the second part of the homework. It also adds the keys for when we join the 3 databases together.

```{r}
gse <- as.data.table(dbGetQuery(geo_con, "SELECT * FROM gse"))
gse_gpl <- as.data.table(dbGetQuery(geo_con, "SELECT * FROM gse_gpl"))
gpl <- as.data.table(dbGetQuery(geo_con, "SELECT * FROM gpl"))
setkey(gse,"gse")
setkey(gse_gpl,"gpl")
setkey(gpl,"gpl")
```

This joins the databases and then outputs the results.
```{r}
dt_join1 <- gpl[gse_gpl,nomatch=0]
setkey(dt_join1,"gse")
dt_join2 <- dt_join1[gse,nomatch=0]
res2 <- dt_join2[pubmed_id=="23067362"][manufacturer %like% "Illumina", list(gse,title,gpl,manufacturer,description)]
res2
```
